### 2016-08-15 ms/ms.tex
added marilia edits

We use NODF (weighted or unweighted) to evaluate network nestedness
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and the distribution of the interaction
frequencies \citep{Galeano2009}. Lastly, Network specialization was
measured using H2, which estimate the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from 0 for generalized
networks to 1 for specialized networks.

\subsection*{Network robustness}

Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness. First, following
\cite{Memmott2004}, we simulate the extinction of plant species the
subsequent extinction cascades of pollinator species. Because the
reproduction of plant species if facilitated by active restoration
efforts, it is unlikely the extinction of pollinators would effect
plant populations in the hedgerows. However, plants ceasing to bloom,
for example in response to drought, will likely effect the pollinators
that depend on them. Plants species were eliminated based on their
degree or abundance, and the number of pollinators that secondarily
went extinct is calculated. The area below the extinction curve is
used as a measure of network robustness \citep{Memmott2004}.

%% Marilia add perturbation methods here

>>>>

We use NODF (weighted or unweighted) to evaluate network nestedness
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and the distribution of the interaction
frequencies \citep{Galeano2009}. Lastly, Network specialization was
measured using H2, which estimate the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from 0 for generalized
networks to 1 for specialized networks.
\subsection*{Network structure}

The changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular community
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid, nestedness would increase
through time. Alternatively, if the network is accumulating specialist
species or if species are beginning to limit their interaction niche
breath as the network assembles, this would lead to an increase in the
network-level specialization \citep{bluthgen-2006-9} and nestedness
would decrease through time. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading effects. Following \cite{Memmott2004}, we simulate
the extinction of plant species the subsequent extinction cascades of
pollinator species. Because the reproduction of plant species if
facilitated by active restoration efforts, it is unlikely the
extinction of pollinators would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on
them. Plants species were eliminated based on their degree or
abundance, and the number of pollinators that secondarily went extinct
is calculated. The area below the extinction curve is used as a
measure of network robustness \citep{bipartite}.

We also explored how the robustness to cascading effects changed as
community assembled, using algebraic connectivity--- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic}--- as a proxy for network robustness
(e.g. Gaiarsa et al., submitted). Algebraic connectivity was first
used to describe spectral properties of complex graphs other than
ecological networks, and it is related to how difficult it is to turn
a network into completely disconnected groups of nodes, or species
\citep{fiedler1973algebraic, costa2007characterization}, and also to
flows in . The larger the algebraic connectivity, the more robust a
network is to perturbations (e.g. Gaiarsa et al., submitted).
